Fast Radio Burst Cosmology

### 2014-04-30 writeup/dm_angular_ps.tex
Wrote down estimators.

\newcommand{\ud}{\,\mathrm{d}}

@@

The covariance matrix is
\begin{align}
    C_{ij} \equiv& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j
    \rangle\\
    =&
        \begin{cases}
            w(\hat{n}_i\cdot\hat{n}_j)
                &  \text{if } (i \neq j) \\
            \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src}
                + \textrm{(the $w$ term)}
                &  \text{if } (i = j)
        \end{cases}
\end{align}

Now that we have the covariance matrix, we construct a quadratic estimator for
chosen parameters $\lambda_\alpha$. The estimator is Equation~11.94 from
Dodelson, although we have to modify it slightly to exclude the
auto-correlations.  The error (assuming Gaussianity) is Equation~11.100.

>>>>

% shortcuts
\newcommand{\ud}{\,\mathrm{d}}
\newcommand{\bD}{\boldsymbol D}
\newcommand{\bC}{\boldsymbol C}
\newcommand{\bDelta}{\boldsymbol \Delta}

% for draft comments.
\newcommand{\red}{\textcolor{red}}
\newcommand{\blue}{\textcolor{blue}}
\newcommand{\green}{\textcolor{green}}

@@

The covariance matrix is
\begin{align}
    C_{ij} \equiv& \langle D_i D_j \rangle - \langle D_i \rangle \langle D_j
    \rangle\\
    =&
        \begin{cases}
            \sum_l \frac{2l+1}{4 \pi} C_l P_l(\hat{n}_i\cdot\hat{n}_j)
                &  \text{if } (i \neq j) \\
            \sigma_{\bar{n}_e}^2 + \sigma^2_{\rm src}
                + \textrm{(the $w$ term)}
                &  \text{if } (i = j)
        \end{cases}
\end{align}

\red{The cosmological term is probably negligible for the diagonal elements.}

We have written the covariance matrix in terms of $C_l$, the
redshift distribution function for FRBs, $p(z)$, and the unknown parameter
$\sigma^2_{\rm src}$.  This will enable us to construct a quadratic estimator
for a desired set of cosmological parameters from the observed set of
dispersion measures.

Now that we have the covariance matrix, we construct a quadratic estimator
($\hat{\lambda}_\alpha$) for
chosen parameters $\lambda_\alpha$. The estimator is Equation~11.94 from
Dodelson, although we have to modify it slightly to exclude the
auto-correlations.  The error (assuming Gaussianity) is Equation~11.100.

Defining data vector $\bDelta = \bD - \bar{D}$ where $\bar{D}$ is the sample
mean of dispersion measures.

\begin{equation}
    \hat{\lambda}_\alpha = \lambda_0
    + \frac{F^{-1}_{\alpha\beta}}{2} 
    \left[ \bDelta^t \bC^{-1} \bC_{,\beta} \bC^{-1} \bDelta
    - \mathrm{Tr}\left[\bC^{-1} \bC_{,\beta}\right] \right],
\end{equation}
for some fiducial value of the parameter $\lambda_0$.  $F_{\alpha\beta}$ is the
Fisher matrix, given by
\begin{equation}
    F_{\alpha \beta} = \frac{1}{2} \mathrm{Tr} 
        \left[ \bC_{,\alpha} \bC^{-1} \bC_{,\beta} \bC^{-1} \right]
\end{equation}

The covariance of this estimator (assuming Gaussianity of the original
data) is
\begin{equation}
    \langle \lambda_\alpha \lambda_\beta \rangle
        - \langle \lambda_\alpha \rangle \langle \lambda_\beta \rangle
        = F^{-1}_{\alpha\beta}
\end{equation}
